---
title: "HW1"
author: "Chen Mo"
date: "9/18/2020"
output: github_document
---

This is my solution to HW1

```{r}
library(tidyverse)
```

##Problem 1
Create a data frame:
```{r}
prob1_df = tibble(
        sample = rnorm(10),
        sample_greater_0 = sample > 0,
        char_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
        fac_vector = factor(c("small", "small", "small", "medium", "medium", "medium", "large", "large", "large", "large"))
)
```

Take the mean of each variable in my data frame:
```{r}
mean(pull(prob1_df, sample))
mean(pull(prob1_df, sample_greater_0))
mean(pull(prob1_df, char_vector))
mean(pull(prob1_df, fac_vector))
```
The mean function works for numbers and logical but not character or factor.

Use as.numeric function to convert variables from one type to another
```{r}
as.numeric(pull(prob1_df, sample_greater_0))
as.numeric(pull(prob1_df, char_vector))
as.numeric(pull(prob1_df, fac_vector))
```
The as.numeric function works for logical and factor but not character.
This means character variables do not have default value in R.

Calculations:
```{r}
as.numeric(pull(prob1_df, sample_greater_0))*pull(prob1_df, sample)
as.factor(pull(prob1_df, sample_greater_0))*pull(prob1_df, sample)
as.numeric(as.factor(pull(prob1_df, sample_greater_0)))*pull(prob1_df, sample)
```


